---
title: "p8105_hw5_tm2680"
author: "Tatini Mal-Sarkar"
date: "11/5/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(stringr)
library(purrr)
library(magrittr)
library(ggridges)
library(httr)
library(dplyr)
```


# Problem 1
```{r long_data_load_tidy}
long_data = str_c("./data/", list.files(path = "./data"))
long_data_df = tibble(long_data)

read_long = function(x) {
  read_csv(x)
}

output = map_dfr(long_data, read_long) %>% 
  mutate(arm = str_sub(long_data, 8, 10),
         arm = replace(arm, arm == "con", "control"),
         arm = replace(arm, arm == "exp", "experimental")) %>% 
  mutate(number = str_sub(long_data, 12, 13)) %>% 
  select(arm, number, everything()) %>% 
  gather(week_1:week_8, key = "week", value = "value") %>%
  janitor::clean_names() %>% 
  separate(week, into = c("drop_var", "week"), sep = "_") %>% 
  select(-drop_var) %>% 
  mutate(week = as.numeric(week))

output %>% 
  ggplot(aes(x = week, y = value, color = number)) +
  geom_line() +
  labs(
    title = "Spaghetti plot of observations over time",
    x = "Week",
    y = "Value"
  ) +
  scale_color_hue(name = "Subject") +
  facet_grid(~ arm)
```

Here is a faceted spaghetti plot showing observations for each subject over a period of 8 weeks. On average, it looks like the values for the experimental group increased over time, whereas the values stayed roughly the same for the control group.


# Problem 2

```{r hom_load_tidy}
hom_url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

hom_dat = read_csv(hom_url) %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  janitor::clean_names() 

hom_dat %>% 
  group_by(city_state) %>% 
  summarize(n_hom = n(),
            n_hom_unsolv = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest")) %>% 
  knitr::kable(digits = 0)
```

The raw data comprises observations on homicides in numerous cities, including date, victim name, race, and gender, location, and disposition. There are 52,179 observations. The above table shows the total number of homicides and number of unsolved homicides by city.



